Type Classes for Mathematics in Type Theory

### 2010-06-28 jar.tex
Break up overly long sentence.

Taking these conversion functions for granted, we will also need a ``down-to-earth'' representation of the initiality arrows if we are to give a \lstinline|SemiRing|-based definition of the interface for natural numbers. Once again, we introduce an operational type class to represent this particular component:
\begin{lstlisting}
  Class NaturalsToSemiRing (A: Type) :=
    naturals_to_semiring: Π B `{RingMult B} `{RingPlus B} `{RingOne B}
      `{RingZero B}, A → B.
\end{lstlisting}
In order to use this with \lstinline|Initial|, we define an additional conversion instance that takes a \lstinline|NaturalsToSemiRing| along with a proof showing that it yields \lstinline|SemiRing_Morphism|s, and builds an \lstinline|InitialArrow| instance out of it invoking another conversion function that translates concrete \lstinline|SemiRing_Morphism| proofs into univeral algebra \lstinline|Homomorphism|s instantiated with the semiring signature, which make up the arrows in the category.\marginpar{Zin te lang}

>>>>

Taking these conversion functions for granted, we will also need a ``down-to-earth'' representation of the initiality arrows if we are to give a \lstinline|SemiRing|-based definition of the interface for natural numbers. Once again, we introduce an operational type class to represent this particular component:
\begin{lstlisting}
  Class NaturalsToSemiRing (A: Type) :=
    naturals_to_semiring: Π B `{RingMult B} `{RingPlus B} `{RingOne B}
      `{RingZero B}, A → B.
\end{lstlisting}
In order to use this with \lstinline|Initial|, we define an additional conversion instance that takes a \lstinline|NaturalsToSemiRing| along with a proof showing that it yields \lstinline|SemiRing_Morphism|s, and builds an \lstinline|InitialArrow| instance out of it. This conversion instance in turn invokes another conversion function that translates concrete \lstinline|SemiRing_Morphism| proofs into univeral algebra \lstinline|Homomorphism|s instantiated with the semiring signature, which make up the arrows in the category.
